\documentclass[10pt,a4paper]{moderncv}

\usepackage{verbatim}
\usepackage[gen]{eurosym}
\usepackage{multicol}

\AfterPreamble{\hypersetup{
  pdfauthor={Saeed Mirshekari},
  pdftitle={CV of Saeed Mirshekari},
  pdfsubject={Detailed CV for Saeed Mirshekari},
  urlcolor=blue,
}}
% moderncv themes
\moderncvtheme[blue]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{Saeed}
\familyname{Mirshekari}
%\address{8026 Knights Crossing Dr, O'Fallon MO}
\email{saeed.mirshekari@gmail.com}      
\mobile{+1 (626) 689 5848}                                 
\homepage{smirs.github.io}                
%\extrainfo{\url{http://markliu.me}} % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{\textsc{Objective}}
%Seeking a Data Scientist position in the US that offers growth opportunities and allows me to utilize and develop my skills and experience in a research-based Data Science team.
%\vspace{0.2cm}

\section{\textsc{Summary}}
%\vspace{0.2cm}

Data Scientist with PhD in Astrophysics with 2 years post doctoral experience in academia (Data Analysis team of \href{http://www.ligo.org}{LIGO}) and 3+ years of work experience in industry. 10+ years of successful research experience in both theoretical and computational physics. Strong problem–solving and leadership skills. Looking for new opportunities towards leading small technical, data-science teams.
\vspace{0.2cm}

Advanced programming proficiency. Certified and experienced in Machine Learning and Deep Learning. Self–motivated and fast–learner. Skilled in collaborations, process improvement, with the ability to translate deep technical ideas and new concepts across all organizational levels. Strong skills in prioritizing, organizing, and time management with strong verbal and written communication skills.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{0.2cm}

\section{\textsc{Highlights}}
\vspace{-0.5cm}
\begin{multicols}{2}
\begin{itemize}
%\item 10+ years of successful research experience
\item 5+ years work experience in Data Analysis
\item 20+ presentations in international conferences
%\item 10+ awarded research and travel grants
\item 50+ publications in top science journals
%\item 10+ MOOCs in cutting edge ML \& DL
\item Team lead experience
\end{itemize}
\end{multicols}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{0.2cm}
\vspace{-0.5cm}

\section{\textsc{Work Experience}}
\subsection{\textsc{Full Time Employment}}

\begin{itemize}
%\item 10+ years of successful research experience
\item \textbf{Bayer (Monsanto), St. Louis, MO [Data Scientist] (2017--Present)}

Through several Data Science projects, I helped to bridge from large scale research data (genomics and phenomics) to the commercial side, leading to improve plant breeding cycles and precision breeding. I built and evaluated product Recommender Systems to recommend the best product crops for a given set of field conditions and needs. I also led an initiative on building a broad documentation platform to facilitate knowledge-transfer across the teams within the organization. Within my role, I had the opportunity to successfully lead a small team of data scientists through their projects for 3 months.
\vspace{.2cm}

\item \textbf{Aclara Technologies, St. Louis, MO [Data Scientist] (2016--2017)}

	Using different machine learning algorithms, I built and evaluated predictive models for residential electricity consumption based on historical data in combination with auxiliary forecasted weather data. In separate projects, I developed web-based platforms to fully visualize electric distribution networks (GIS) and anomaly detection via clustering algorithms. I had a major role in the development of Aclara Fault Detection and Localization's core algorithm (Bayesian Network \& Information Theory) and all its data analysis.
\vspace{.2cm}

\item \textbf{ICTP-SAIFR, S\~{a}o Paulo, Brazil [Postdoctoral Research Fellow] (2013--2015)}

	As a researcher/developer in Data Analysis team of LIGO scientific collaboration, I helped developing and testing various data analysis algorithms and signal processing pipelines. I designed and performed a comprehensive, complex computational analysis to quantitatively investigate the accuracy of gravitational-wave signal template models to be used in searches for extremely weak gravitational-wave signals from compact celestial objects such as black-holes and neutron-stars.

\vspace{.2cm}
\item \textbf{Washington University in St. Louis, MO [Research Assistant] (2009--2013)}

	I did advanced research and teaching in the field of theoretical physics. In my dissertation, I obtained the equations of motion for compact binary objects such as black-holes under alternative theories of gravity beyond General Relativity. The results of this study are required by current gravitational-wave observatories such as LIGO to test fundamental laws of physics in strong gravitational field regimes such as in spaces near black-holes and neutron-stars.
\end{itemize}

%\vspace{0.1cm}
%\subsection{\textsc{Data Scientist (2015--present)}}

%\cventry{}{Bayer (Monsanto), St. Louis, MO}{}{}{}{}{}
%2+ years working experience with severals of different datasets in order to clean, analyze, visualize, and model them to bridge from large scale genetic and phenotypic breeding testing data and bring insight to the business. Using different machine learning algorithms, I built and evaluated product recommender systems based on historical testing data to recommend the best products which fit the growers’ conditions and needs the best. I also led an initiative on building a documentation center to facilitate knowledge-transfer across the teams in the organization.
%\begin{itemize}
%\item 2+ years active working experience using Python, R, R-shiny
%\item Delivered several hands-on tutorials to breeders and analysts outside our team on my developed projects.
%\end{itemize}

%\cventry{}{Aclara Technologies, St. Louis, MO}{}{}{}{}{}
%{1+ year working experience with severals of different datasets in order to clean, analyze, visualize, and model them. Using different machine learning algorithms, I built and evaluated predictive models for residential electricity consumption based on historical data in combination with auxiliary forecasted weather data. In separate projects, I developed web-based platforms to fully visualize electric distribution networks (GIS) and network anomaly detection via clustering algorithms. I have been extensively involved in the development of Aclara Fault Detection and Localization's core algorithm (Bayesian Network \& Information Theory) and all it's data analysis.}
%\vspace{0.2cm}
%\begin{itemize}
%\item 1+ year active working experience using R and MATLAB
%\item Delivered several hands-on tutorials to engineers and analysts outside our team on my developed projects.
%\item Delivered 2+ presentations in R\&D technical seminars.
%\item Co-author of one pending US patent in Smart Grid and the following technical reports.
%\end{itemize}

%\vspace{0.4cm}
%\subsection{\textsc{Postdoctoral Research Fellow (2013--2015)}}
%\cventry{}{}
%ICTP South American Institute for Fundamental Research, S\~{a}o Paulo, Brazil}{}{}{}{}
%{2 years working experience as a researcher/developer in data analysis team of LIGO scientific collaboration to develop and test various data analysis algorithms and signal processing pipelines. I designed and performed a comprehensive, complex computational analysis to quantitatively investigate the accuracy of gravitational-wave signal template models to be used in searches for extremely weak gravitational-wave signals among noisy detectors' data in gravitational-wave observatories. Other activities and achievements include:
%\vspace{0.2cm}
%\begin{itemize}
%\item Published 5 research articles in refereed scientific journals.
%\item 2 years everyday working experience using Python
%\item Delivered 5+ presentations in international seminars, workshops, and conferences.
%\item Assisted in grant writing and preparation for external funding opportunities (2/2 proposals got funded).
%\item Awarded prestigious FAPESP postdoctoral research fellowship plus generous annual travel grants.
%\item Qualified and awarded full travel grants to visit LIGO Lab in Caltech and to attend international conferences.
%\item Served 2 years as the organizer of biweekly Astrophysics Journal Club to bring local experts together.
%\end{itemize}

%\vspace{0.4cm}
%\subsection{\textsc{Research Assistant (2009--2013)}}
%\cventry{}{Physics Department, Washington University in St. Louis, MO}{}{}{}{}
%{Designed and executed research studies on Einstein's General Relativity via advanced, complex analytical analysis. Successfully awarded a Ph.D. in Physics under \href{http://www.phys.ufl.edu/~cmw/}{Prof. Clifford Will} in only nine semesters with excellent grades and records. Specific activities included:}
%\vspace{.2cm}

%\begin{itemize}
%\item Accomplished three research projects via performing advanced, complex, analytical analysis.
%\item Published 3 research articles in top scientific journals.
%\item Delivered 15+ presentations in high quality, national and international seminars, workshops, and conferences.
%\item Taught physics labs for two semesters and assisting in teaching Astronomy courses.
%\item Awarded university fellowship and tuition waiver for excellent performance in coursework and research.
%\item Qualified and awarded travel grants from American Physics Society (3 times, $\sim$\$1k each)
%\item Served two years in Physics Graduate Peer Mentor Program in Washington University in St. Louis
%\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\textsc{Visiting Research Scholar}}
\begin{itemize}
\item \textbf{Caltech} Institute of Technology, Pasadena, CA (Mar 2015) %(March 20--27, 2015)
\item \textbf{University of Wisconsin-Milwaukee}, Milwaukee, WI (Jan--Feb 2014 \& Sep 2014) %(September 1--30, 2014 \& January 13--February 5, 2014)
\item \textbf{University of Florida}, Gainesville, FL (Nov 2012 to Aug 2013) %(November 1, 2012--August 30, 2013)
\item \textbf{Institut d'Astrophysique de Paris}, Paris (July--Sep 2012) %(July 2--September 18, 2012)
\item \textbf{MIT} Kavli Institute, Boston, MA (Mar 2011)%(March 16--27, 2011)
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{\textsc{Participation in Data Analysis Meetings of LIGO}}
%\begin{itemize}
%\item Caltech Institute of Technology, Pasadena, CA (March 15--19, 2015)
%\item Stanford University, Stanford, CA (August 25--29, 2014)
%\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{.2cm}
\section{\textsc{Education}}
\begin{itemize}
\item Ph.D. in Physics, Gravitation \& Astrophysics, Washington University in St. Louis, MO (2013)
\item M.Sc. in Physics, Gravitation \& Astrophysics, University of Tehran, Iran (2008)
\item B.Sc. in Physics, Solid State, University of Tehran, Iran (2005)
\end{itemize}

%\cventry{2013}{Ph.~D. in Physics}{Washington University in St. Louis, MO}{}{}{}{}
%{Clifford M. Will}}
%{Dissertation: Gravitational Waves and Inspiraling Compact Binaries in Alternative Theories of Gravity\\Advisor: \small Prof. \href{http://www.physics.wustl.edu/cmw/}
%\cventry{2008}{M.~Sc. in Physics}{University of Tehran, Iran}{}{}{}{}
%{Amir M. Abbassi}} 
%{Thesis: Energy-momentum Prescriptions in Non-static Space-times\\Advisor: \small Dr. \href{http://physics.ut.ac.ir/pages/faculty.html}
%\cventry{2005}{B.~Sc. in Physics}{University of Tehran, Iran}{}{}{}{}
% {Advisor: \small Dr. \href{http://physics.ut.ac.ir/~moshfegh/}{Hamid R. Moshfegh}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{.2cm}
\section{\textsc{Computer Skills and Languages}}
\begin{itemize}
\item Programming languages including \textbf{Python}, \textbf{R}, \textbf{MATLAB}, \textbf{C}, plus \textbf{Bash} and \textbf{SQL} [5+ years]
\item Analytical and computational tools including \textbf{Maple} and \textbf{Mathematica} [3+ years]
\item Web-based analytical tools including \textbf{RShiny} and \textbf{AzureML} [1+ years]
%\item Big Data Analysis tools \textbf{MySQL} and \textbf{Hadoop}
\item Distributed computing via \textbf{HTCondor}
\item Version control systems including \textbf{GIT}, \textbf{CVS}, and \textbf{TSF}
\item Typesetting, documentation and report producing tools including \textbf{Sphinx} and \textbf{\LaTeX}\\
\item Full fluency in \textbf{English} and \textbf{Persian}, basic skills in \textbf{Arabic} and \textbf{Portuguese}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{.2cm}
\section{\textsc{Certificates in Data Science [MOOCs]}}
%\cventry{2015}{Top 5\% in Kaggle competition: Coupon Purchase Prediction} {}{}{}{[Currently ranked 34th among 712 teams. 16 Jul -- 30 Sep, 2015 (ongoing)]}

\begin{itemize}
\item \textbf{\href{https://www.coursera.org/specializations/tensorflow-in-practice}{TensorFlow in Practice Specialization (2019)} }including 4 courses: [1] Introduction to TensorFlow for Artificial Intelligence, Machine Learning, and Deep Learning, [2] Convolutional Neural Networks in TensorFlow, [3] Natural Language Processing in TensorFlow, [4] Sequences, Time Series and Prediction. All courses offered by deeplearning.ai via Coursera [Instructor: Laurence Moroney]

\item \textbf{\href{https://www.coursera.org/specializations/deep-learning}{Deep Learning Specialization (2018)}} including 5 courses: [1] Neural Networks and Deep Learning, [2] Improving Deep Neural Networks, [3] Structuring Machine Learning Projects, [4] Convolutional Neural Networks, [5] Sequence Models. All courses offered by deeplearning.ai via Coursera [Instructor: Andrew Ng]

\item \textbf{\href{}{Machine Learning (2014-2015)}} including 3 courses: [1] Data Science and Machine Learning Essentials; offered by Microsoft via edX [A 5-week online course, Instructors: Steve Elston and Cynthia Rudin], [2] Statistical Learning; offered by Stanford University via Dataschool.io [A 10-week online course; Instructors: Trevor Hastie and Robert Tibshirani], [3] Machine Learning; offered by Stanford University via Coursera [A 10-week online course; Grade:100\%, Instructor: Andrew Ng]

\item \textbf{\href{}{Data Science Toolbox (2014)}} including 3 courses: [1] The Data Scientists Toolbox; offered by Johns Hopkins University via Coursera [A 4-week online course; Instructors: Roger Peng, Jeff Leek, Brian Caffo], [2] Getting and Cleaning Data; offered by Johns Hopkins University via Coursera [A 4-week online course; Instructors: Roger Peng, Jeff Leek, Brian Caffo], [3] R Programing; offered by Johns Hopkins University via Coursera [A 4-week online course; Instructors: Roger Peng, Jeff Leek, B. Caffo]

\end{itemize} 

%\cventry{2015}{Data Science and Machine Learning Essentials}{Offered by Microsoft via edX}{}{}{[A 5-week online course; Instructors: Steve Elston and Cynthia Rudin]}
%\cventry{2015}{Statistical Learning}{Offered by Stanford University via Dataschool.io}{}{}{[A 10-week online course; Instructors: Trevor Hastie and Robert Tibshirani]}
%\cventry{2014}{Machine Learning}{Offered by Stanford University via Coursera}{}{}{[A 10-week online course; Grade:100\%, Instructor: Andrew Ng]}
%\cventry{2014}{R Programing}{Offered by Johns Hopkins University via Coursera}{}{}{[A 4-week online course; Grade:100\% with Distinction, Instructors: Roger Peng, Jeff Leek, B. Caffo]}
%\cventry{2014}{The Data Scientists Toolbox}{Offered by Johns Hopkins University via Coursera}{}{}{[A 4-week online course; Instructors: Roger Peng, Jeff Leek, Brian Caffo]}
%\cventry{2014}{Getting and Cleaning Data}{Offered by Johns Hopkins University via Coursera}{}{}{[A 4-week online course; Instructors: Roger Peng, Jeff Leek, Brian Caffo]}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{.2cm}
\section{\textsc{Awards}}
\cventry{2016} {Breakthrough Prize in Fundamental Physics}{for the detection of gravitational waves}{}{}{The Breakthrough Prize recognizes the world's top scientists. Each prize is \$3 million and presented in the fields of Life Sciences (up to five per year), Fundamental Physics (up to one per year) and Mathematics (up to one per year).\vspace{0.2cm}\\ \textit{A Special Breakthrough Prize in Fundamental Physics was awarded to 1015 scientists and engineers contributing to the detection of gravitational waves announced in February of 2016.}}

%\vspace{.2cm}
\section{\textsc{Voluntary Activities}}
\cventry{2019} {Data Science Teacher}{CoderGirl}{}{}{CoderGirl is LaunchCode’s education program designed to engage and educate women in the technology community in St. Louis. \vspace{0.2cm}\\ \textit{The program includes a 24-week data-science specialized track designed to equip CoderGirls with technical skills and job-readiness skills, leading up to a apprenticeship job program. CoderGirl provides a space for women of all skill levels to learn to code in a supportive community of like-minded individuals.}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{\textsc{Training and Experience}}
%\cventry{2013-2015}{FAPESP Postdoctoral Research Fellow}{}{}{}{ICTP South American Institute for Fundamental Research}
%\cventry{2013-2015}{Data Analyzer and Developer}{}{}{}{Data Analysis Group of LIGO Scientific Collaboration}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{\textsc{Teaching}}
%\subsection{Washington University, Teaching Assistant:}
%\cvline{}{Astrophysics (2010), General Physics Lab (2009--10)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{University of Tehran, Teaching Assistant:}
%\cvline{}{Mathematical Physics I, II (2007--08), Modern Physics Lab (2003--07), Modern Physics (2005)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{.2cm}
%\section{\textsc{Past Professional Affiliations}}
%\cventry{2015--now}{Data Scientist}{Aclara Technologies LLC}{}{}{}
%\cventry{2013--2015}{Postdoctoral Research Fellow}{ICTP South American Institute for Fundamental Research}{}{}{}
%\cventry{2013--2015}{Researcher/Code-Developer}{LIGO data analysis group}{PyCBC Python toolkit}{}{}
%\cventry{2012--2013}{Visiting Research Scholar}{University of Florida}{}{}{}
%\cventry{2009--2013}{Research Assistant and Graduate Student}{Washington University in St. Louis}{}{}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}